Community Health Councils, Inc. (CHC) is a non-profit, community-focused health education and policy organization.  Founded in 1992, they strive to advance social justice and increase access to healthcare resources for economically-disadvantaged populations.  They are organized into four main policy areas.
	\paragraph{Access and Quality of Healthcare Coalitions} Organize existing community leadership to improve the quality of healthcare services in South Los Angeles.  It has two coalitions, the Coalition for Health and Justice and the South Los Angeles Healthcare Leadership Roundtable, which taps into healthcare leaders in the neighborhood to help create an effective, accessible health care system for the South Los Angeles community.
	\paragraph{Expansion and Quality of Healthcare Coverage} Supports local and state coalitions to expand outreach, enrollment, and retention in public healthcare programs.  Covering Kids and Families California seeks to expand coverage by reducing barriers to enrollment in health coverage programs.  LA Access to Health Care Coverage Coalition represents over 40 community organizations representing low-income, uninsured families.  Accessing Benefits for Children is an outreach program that helps families utilize low-cost health coverage. 
	\paragraph{Nutrition Resource Development} Works with South Los Angeles locals to advocate for expanding open space and food resources.  The Food Policy Roundtable is a coalition to improve food availability, affordability and access in local grocery stores. 
	\paragraph{Environmental Health} Seeks to improve the physical community in many ways.  These include reducing pollution, converting vacant lots to green space, streetscape improvement that improve mobility, and health-promoting land-use standards.  The Coalition for an Active South LA brings together local residents and organizations to make the surroundings more compatible with physical activity. 
	 
	Through these four policy areas and numerous coalitions, CHC takes an active role in leading the way for a more healthy and livable South Los Angeles.