\documentclass{letter}


\signature{Jake Hermle\\Nakul Joshi\\John Lally\\Christine Noh }
\address{University of Southern California\\Los Angeles\\California 90007}
\date{6\textsuperscript{th} December 2013}

\begin{document}

\begin{letter}{Community Health Councils, Inc.\\3731 Stocker Street,\\ Suite 201\\ Los Angeles, CA 90008}
\opening{To whom it may concern,}

We are four students at University of Southern California expected to graduate next year, May of 2014. With each of us majoring in a different subfield/subject, we tried to see this project from various perspectives in order to seek what fits best for CHC. 

After the insightful site visit, we decided to target ways in which we can improve pedestrian and biker safety as well as for mobility as a whole for the greater Los Angeles. With many traffic-calming techniques already available, we have narrowed down the list to eight specific techniques that we found to be the most reliable and efficient and analyzed them thoroughly. Those eight techniques are chokers, curb radius, raised crosswalks, curb extensions, textured pavements, dignified zones, traffic circles, and midblock crossings. After going deeply into each technique, we have ranked them from top to bottom for you to easily be able to see which ones are the most suitable for Los Angeles. 

We have focused this project to cater to CHC’s needs and we hope that you find this information helpful for your future plans and projects. Furthermore, we have included references for you to be able to easily find additional information on the given practices. Thank you so much for taking the time to answer our emails whenever we needed any clarifications.

\closing{Sincerely,}
\end{letter}

\end{document}
